### 2016-05-20 paper/paper.tex
Fixes

An interesting choice in the design of DDoSCoin is that the target-setting is done 
dynamically, and by consensus. A given target can go offline, or in some other way
defend against DDoSCoin at any point. When this happens, the currency cannot stall,
as then no coins could be transacted. This necessitates dynamic target-setting, 
despite how strange it may be to have the ``goalposts'' move on miners. This places
risk in targetting sites that are likely to be removed from the target list, or
\emph{controversial} sites. However, each site has its difficulty adjusted 
individually, the controversial site will be easier to mine a block from as more 
miners shy away, balancing the affect.

While stakeholders have control of the target list, a majority of miners could
use their choice of previous block to veto a given proof-of-stake block. This would
be a fork of the blockchain. If a clear majority treat a block as malformed because
it introduces an undesired domain, then the longer chain wins, and the undesired
domain is not included in the target set, and any blocks mined on the chain with
the vetoed target are not part of the blockchain.

>>>>

An interesting choice in the design of DDoSCoin is target-setting is done 
dynamically, and by consensus. A given target can go offline, or in some other way
defend against DDoSCoin at any point. When this happens, the currency cannot stall,
as then no coins could be transacted. This necessitates dynamic target-setting, 
despite how strange it may be to have the ``goalposts'' move on miners. This places
risk in targetting sites that are likely to be removed from the target list, or
\emph{controversial} sites. However, each site has its difficulty adjusted 
individually, the controversial site will be easier to mine a block from as more 
miners shy away, balancing the affect.

While stakeholders have control of the target list, a majority of miners could
use their choice of previous block to veto a given proof-of-stake block. This would
be a fork of the blockchain. If a clear majority treat a block as malformed because
it introduces an undesired domain, then the longer chain wins, and the undesired
domain is not included in the target set, and any blocks mined on the chain with
the vetoed target are not part of the blockchain. This allows the miners to coordinate
and self-enforce a blacklist, or whitelist, of target domains, so long as they 
have sufficient participation in the policy.
